The Impact of Alternation

### 2017-05-10 draft.tex
ok

We consider a total alphabetical order $\prec$ on $\Sigma$ and lift it
to the total lexicographical order $\prec^*$ on $\Sigma^*$. We write
$n \prec^* m$ if the sequence labeling the path from $\rootNode$ to
$n$ is strictly smaller, in the lexicographical order, than the
sequence labeling the path from $\rootNode$ to $m$. A node $n \in N$
is \emph{covered by $m$} if $(n,m) \in \lhd$. We say that $n$ is just
\emph{covered} when $m$ is not important. A node $n$ is \emph{closed}
if for all nodes $m \in N$ such that $n \prec^* m$, either $\Lambda(n)
\not\models \Lambda(m)$ or $(n,m) \in \lhd$ holds. To efficiently
check that a node is closed, one may keep all the nodes from the ART
in a list, in preorder.

@@

  \For{$a \in \Sigma$} 
  \Comment{expand $n$}

@@

  \State enqueue $s$ into $\worklist$

@@

Finally, we expand $n$ (lines \ref{ln:expand-begin} -
\ref{ln:expand-end}) by creating a new node for each successor via an
input event $a \in \Sigma$ and inserting it into the worklist. The
label of the

>>>>

We consider a total alphabetical order $\prec$ on $\Sigma$ and lift it
to the total lexicographical order $\prec^*$ on $\Sigma^*$. We write
$n \prec^* m$ if the sequence labeling the path from $\rootNode$ to
$n$ is strictly smaller, in the lexicographical order, than the
sequence labeling the path from $\rootNode$ to $m$.

A node $n \in N$ is \emph{covered} if it has an ancestor $m$ such that
$(m,p) \in \lhd$, for some $p \in N$. A node $n$ is \emph{closed} if
it is covered, or $\Lambda(n) \not\models \Lambda(m)$ for all $m \in
N$ such that $n \prec^* m$.

@@

  \For{$a \in \Sigma$} 
  \Comment{expand $n$}
  \label{ln:expand-begin}

@@

  \State enqueue $s$ into $\worklist$
  \label{ln:expand-end}

@@

Finally, we expand $n$ (lines \ref{ln:expand-begin} -
\ref{ln:expand-end}) by creating a new node for each successor $s$ via
an input event $a \in \Sigma$ and inserting it into the worklist. The
label of the new node is $\top$, its replacement set $R(s)$ is
computed based on $R(n)$ and the label of the edge $(n,a,s)$ is
$\Theta(n,k)$, where $k$ is the level of $n$ in $\Art$.
